DOpElib:\\ Differential Equations and Optimization Environment

### 2017-04-13 Examples/Documentation/examples.tex
Updated docu w.r.t. to linker errors while using the wrong deal.II library
Updated documentation at several places

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{How to run existing examples}
The easiest way is to first build all examples. Go into 
\begin{lstlisting}
dopelib/Examples/
\end{lstlisting}
Herein, type 
\begin{lstlisting}
make c-all
\end{lstlisting}
By typing only `make' you will see all options.
This procedure will take some minutes. Afterwards,
go into the examples folder of your choice. For instance:
\begin{lstlisting}
dopelib/Examples/PDE/InstatPDE/Example1
\end{lstlisting}
Herein you create the executable via
\begin{lstlisting}
make 
\end{lstlisting}
and then 
\begin{lstlisting}
./DOpE-PDE-InstatPDE-Example1 
\end{lstlisting}
Or both commands together:
\begin{lstlisting}
make && ./DOpE-PDE-InstatPDE-Example1 
\end{lstlisting}
You will find the results on the screen in the terminal as well
as some graphical output in the `Results' folder.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Changing from Release mode to Debug mode}
In a specific example go into the autobuild folder 
and change therein:
\begin{lstlisting}
CMAKE_BUILD_TYPE:STRING=Release
\end{lstlisting}
to 
\begin{lstlisting}
Debug Release RelWithDebInfo MinSizeRel
\end{lstlisting}
Then go one folder back and type as usual `make' to build the executable file.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{How to run existing examples}
\subsection{The global way}
The easiest way is to first build all examples. Go into 
\begin{lstlisting}
dopelib/Examples/
\end{lstlisting}
Herein, type 
\begin{lstlisting}
make c-all
\end{lstlisting}
By typing only `make' you will see all options 
(we also refer to Section \ref{sec_installation}).
This procedure will take some minutes. Afterwards,
go into the examples folder of your choice. For instance:
\begin{lstlisting}
dopelib/Examples/PDE/InstatPDE/Example1/autobuild
\end{lstlisting}
Herein you create the executable via
\begin{lstlisting}
make 
\end{lstlisting}
and then go back via ../ and 
\begin{lstlisting}
./DOpE-PDE-InstatPDE-Example1 
\end{lstlisting}
Or both commands together:
\begin{lstlisting}
autobuild> make && cd .. &&  ./DOpE-PDE-InstatPDE-Example1 
\end{lstlisting}
You will find the results on the screen in the terminal as well
as some graphical output in the `Results' folder.

\subsection{Building, making and running in the local folder}
In case we have run first globally as previsously described, 
in each examples folder we find an autobuild subfolder. 
If we now want to work locally (which is the usual way) then 
we have to type `make' in the autobuild folder:
\begin{lstlisting}
autobuild> make
\end{lstlisting}
In case we need to modify the Makefile, we need first to do:
\begin{lstlisting}
autobuild> cmake ..
\end{lstlisting}
For instance one reason to modify the Makefile could be 
to change to debug mode as described in Section \ref{sec_release_debug}.
Finally, go one folder back and run the object file.

In case you work and test out new things (modifiying the 
main.cc and localpde.h files etc.), one command for instance 
in Example 9 is:
\begin{lstlisting}
Example9> cd autobuild/ && make && cd .. &&  ./DOpE-PDE-StatPDE-Example9
\end{lstlisting}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Changing from Release mode to Debug mode}
\label{sec_release_debug}
In a specific example go into the autobuild folder 
and change therein:
\begin{lstlisting}
cmake CMAKE_BUILD_TYPE=Release ..
\end{lstlisting}
to some other behavior:
\begin{lstlisting}
Debug Release RelWithDebInfo MinSizeRel
\end{lstlisting}
Then type `make' to build the executable file and go back 
into the parent folder and execute the object file.

### 2017-04-13 Examples/PDE/StatPDE/Example9/content.tex
Updated documentation at several places

\subsubsection{General problem description}
\index{stationary PDE}\index{stationary PDE!FSI problem} \index{fluid} \index{fluid!incompressible} \index{fluid!Newtonian}
In this example we consider a simple stationary FSI problem. The fluid
is given as an incompressible Newtonian fluid modeled by the Stokes equation. Here, we use the symmetric stress tensor which has a little consequence when using the do-nothing outflow condition, see also section \ref{PDE_Stat_Stokes}.
The computation domain is $\Omega = [-6,6]\times [0,2]$ and we choose for simplicity $f=0$.

@@

The structure equations are given by incompressible neo-Hookean material
\index{structure} \index{structure!incompressible neo-Hookean (INH) material} \index{structure!Lagrangian framework}
\begin{Problem}[Incompressible neo-Hookean Model (Lagrangian)]
  \begin{equation*}
    \begin{aligned}
      (\hat J_s \hat\sigma_s \hat F_s^{-T},\hat\nabla\hat\phi^v)_{\hat\Omega_s}
      &= \langle\hat J_s\hat n_s\cdot \hat g_s^\sigma\hat
      F_s^{-T},\hat\phi^v  \rangle_{\hat\Gamma_i}
      &&\quad\forall\hat \phi^v\in\hat V_s\\
      %%%%%%%%%%%%%%%% 
      (\hat v_s,\hat\phi^u)_{\hat\Omega_s}&=0
      &&\quad\forall\hat \phi^u\in\hat V_s    ,\\
      (\hat J-1,\hat\phi^p)_{\hat\Omega_s} &=0
      &&\quad\forall\hat \phi^p\in\hat L_s,\\
    \end{aligned}
  \end{equation*}
  where $\rho_s$ is the solid's density, $\mu_s$ the Lam\'e
  coefficient, $\hat n_s$ the outer normal vector at $\hat\Gamma_i$, 
  $\hat g_s^\sigma$ the force on the interface and with  
  \[
  \hat\sigma_s:=-\hat p_sI+\mu_s(\hat F_s\hat F_s^T-I).
  \]
\end{Problem}

@@

%%% Unsinn! Das example hat nicht viel mit dem davor zu tun!
%There is not much difference to the prior example, so we will keep our remarks rather short. The \textit{functionals.h} and \textit{myfunctions.cc} files did not change at all, so we simply refer to the corresponding sections in the last example.\\
In the \textit{localpde.h} file, all functions of the \texttt{LocalPDE} class have to be adjusted to the current FSI problem. This only makes the equations and matrices a little more complicated, and our solution vector now consists of five components (two velocity components of the fluid, the pressure component, and two additional displacement components for the structure variables). Otherwise, everything is analogous to the former example.\\
In the \textit{main.cc} we only have to add two components to the \texttt{compmask} vector and prescribe boundary conditions for the structure variables. Apart from that, we define objects for the same classes as before that are even named equally and use the same solvers.\\ 
Again, the solution is reached within one Newton step, and all we see from the program output is the values of the functionals.

>>>>

\subsubsection{General problem description}
\index{stationary PDE}\index{stationary PDE!FSI problem} \index{fluid} \index{fluid!incompressible} \index{fluid!Newtonian}
In this example we consider a simple stationary FSI problem. The fluid
is given as an incompressible Newtonian fluid modeled by the Stokes
equation. Here, we use the symmetric stress tensor which has a little
consequence when using the do-nothing outflow condition, see also
section \ref{PDE_Stat_Stokes}. The flow is driven by non-homogeneous Dirichlet 
condition on the left bounddary.

The computation domain is $\Omega = [-6,6]\times [0,2]$ and we choose for
simplicity $f=0$. 
We add in the subdomain $\Omega_s = [0,2]\times [0,1]$ a solid obstacle. In
this 
solid we prescribe an incompressible neo-Hookean material law.

@@

The structure equations are given by incompressible neo-Hookean material
\index{structure} \index{structure!incompressible neo-Hookean (INH) material} \index{structure!Lagrangian framework}
\begin{Problem}[Incompressible neo-Hookean Model (Lagrangian)]
  \begin{equation*}
    \begin{aligned}
      (\hat J_s \hat\sigma_s \hat F_s^{-T},\hat\nabla\hat\phi^v)_{\hat\Omega_s}
      &= \langle\hat J_s\hat n_s\cdot \hat g_s^\sigma\hat
      F_s^{-T},\hat\phi^v  \rangle_{\hat\Gamma_i}
      &&\quad\forall\hat \phi^v\in\hat V_s\\
      %%%%%%%%%%%%%%%% 
      (\hat v_s,\hat\phi^u)_{\hat\Omega_s}&=0
      &&\quad\forall\hat \phi^u\in\hat V_s    ,\\
      (\hat J-1,\hat\phi^p)_{\hat\Omega_s} &=0
      &&\quad\forall\hat \phi^p\in\hat L_s,\\
    \end{aligned}
  \end{equation*}
  where $\rho_s$ is the solid's density, $\mu_s$ the Lam\'e
  coefficient, $\hat n_s$ the outer normal vector at $\hat\Gamma_i$, 
  $\hat g_s^\sigma$ the force on the interface and with  
  \[
  \hat\sigma_s:=-\hat p_sI+\mu_s(\hat F_s\hat F_s^T-I).
  \]
\end{Problem}
\begin{remark}
At our developer meeting on Apr 13, 2017, we also added 
a simplified STVK material for testing purposes. This STVK 
material is implemented in a different header file (see also 
further comments below).
\end{remark}

@@

In the \textit{localpde.h} file, all functions of the \texttt{LocalPDE} class have to be adjusted to the current FSI problem. This only makes the equations and matrices a little more complicated, and our solution vector now consists of five components (two velocity components of the fluid, the pressure component, and two additional displacement components for the structure variables). Otherwise, everything is analogous to the former example.\\
In the \textit{main.cc} we only have to add two components to the \texttt{compmask} vector and prescribe boundary conditions for the structure variables. Apart from that, we define objects for the same classes as before that are even named equally and use the same solvers.\\ 
Again, the solution is reached within one Newton step, and all we see from the
program output is the values of the functionals.

We also demonstrate another very convenient feature. Since we have 
two different material laws (INH and simplified STVK), we do not implement 
them together in one \textit{localpde.h} file by using if-conditions etc. 
But we implement them seperately in two different *.h files, namely
\begin{lstlisting}
localpde.h
localpde_stvk_material.h
\end{lstlisting}
In the \texttt{main.cc} function we can now simply comment 
or uncomment the respective file we want to work with.
This allows us to keep a clean file for a running example and experiment 
in other files (possibly more than $2$) and by just changing 
two lines in the main.cc in order to change the equations.
